---
title: "A colored 3D plot"
description: |
author:
  - name: Xi Yang
    url: 
date: 03-20-2019
output:
  distill::distill_article:
    self_contained: false
    
categories:
  - Data_viz
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, layout = "l-screen"}
# make a colored 3Dplot with alpha = .05, pH1 = .8
x<-seq(0, 1, 0.1)
y<-seq(0, 1, 0.1)
BayesRatioModelSet <- function(x, beta, alpha=.05, pH1=.8, print = TRUE){
  a <- dbinom(x*10, 10, prob = alpha) 
  #a <- p (these results | H0 true)
  b <- dbinom(x*10, 10, prob = beta)
  #b <- p (these results | H1 true)
  c <- b/a*pH1/(1-pH1)
  #c <- Bayes Theorem odds ratio of H1:H0
  return(log10(c+1))}
z = outer(x,y,BayesRatioModelSet)
# Surface colours corresponding to z-values
nrz <- nrow(z)
ncz <- ncol(z)
jet.colors <- colorRampPalette( c("blue", "green"))
nbcol <- 100
color <- jet.colors(nbcol)
zfacet <- z[-1, -1] + z[-1, -ncz] + z[-nrz, -1] + z[-nrz, -ncz]
facetcol <- cut(zfacet, nbcol) 
persp(x, y, z, col = color[facetcol],
      xlab = "power",
      ylab = "proportion",
      zlab = "Log10(BayesRatio+1)",
      main = "BayesRatioDependingonProportionPowerAlphapH1",
      theta=30,phi=30,ticktype="detailed",
      d = 1)
```

This is an example of a colored 3Dplot with alpha = .05, pH1 = .8. 
The x-axis is the statistical power;
The y axis is the proportion of the experiments found statistically significant results;
The z axis is the probability that the experiment finding is actually true (the effect in reality exsits).

As you can see from the plot, 
given the alpha and base rate (pH1) assumptions, 
when power is equal to the proportion of the significant experiments, 
the probability that the experiment finding is actually true is highest...
Unlike the common myth, 
where many people believe that the higher the statistical power, 
the more likely the significant finding is true.


